### 2021-10-18 documentos/vector_space.tex
Primeros comentarios

\subsection{A vector space of channels} % {{{
\cpnote{Quiza falta lo de las clases de equivalencias}\par
% Inversion de la relacion entre tau y p, y que las probablidiades deben ser positivas {{{
The problem of determining complete positivity of a PCE can be recast as 
determining which vectors $\vtau$ are mapped via
$\san$
% \begin{equation}
% \san\vec\tau=2^N\vec p
% \label{eq:condition}
% \end{equation}
to a vector with positive entries $\lambda_\valpha$, as in \eref{eq:lambda:is:A:tau}. 
% . In components, this would read 
% \begin{equation}
% % \left(
% \sum_\vbeta
% \san_{\valpha\vbeta} \,
% % \right)
% \tau_{\vec \beta}=2^Np_{\vec\alpha}
% \label{eq:A:tau:is:p}
% \end{equation}
% where
% $\san_{\vec\alpha\vec\beta} =\sa_{\alpha_1\beta_1}\cdot\ldots\cdot
% \sa_{\alpha_N\beta_N}$. 
Using the fact that $a^{-1}=a/4$, so 
% (so $A = A^{-1}/2^N$) 
\begin{equation}
A^{-1} = \frac{1}{4^N} A
\end{equation}
we can directly invert \eref{eq:lambda:is:A:tau} to obtain 
\begin{equation}
% \tau_{\vec \alpha}= \san_{\vec\alpha\vec\beta} \, p_\vbeta,
% \tau = 
% \san \lambda =2^N \tau
\sum_\vbeta \san_{\valpha \vbeta} \lambda_\vbeta =2^N \tau_\valpha
\label{eq:tau:is:A:p}
\end{equation}
which will serve as a starting point for our analysis. 
This is a remarkable equation, as it provides a method to diagonalize any diagonal 
Pauli channel, as in \eref{eq:definition:Pauli}.

Other two simple but crucial
observation are the following. For valid quantum channels, 
% \begin{equation}
% % \sum_{
% \end{equation}
$\sum_{\valpha \in \Omega} \lambda_\valpha=0$ implies that 
$\lambda_\valpha=0$ for all $\valpha\in \Omega$, as each member of the sum 
greater or equal to zero, 
% $p_{\vec\alpha}+p_{\vec\beta}=0$ implies $p_{\vec\alpha}=p_{\vec\beta}=0$, as
% all $p_{\vec\alpha} \ge 0$
due to complete positivity of the underlying channel. 
Finally, looking into the first component of \eref{eq:tau:is:A:p}, and taking into 
account the normalization condition that $\tau_{\vec 0}=1$, we obtain
\begin{equation}
\sum_\valpha \lambda_\valpha = 2^N,
\label{eq:sum:alpha:is:2N}
\end{equation}
since, $A_{\vec 0, \vbeta}=1$ for all $\vbeta$. \par
% }}}
% Conexion de los indices para llegar al grupo de Klein {{{
Now we need a definition: to each multi-index $\vec\alpha$ we associate a \textit{set}
of multi-indices $\Phi(\vec\alpha)$ as follows
\begin{equation}
\Phi(\vec\alpha):=\left\{
\vec\beta:\san_{\vec\alpha\vec\beta}=1
\right\}
% =\left\{ \vec\beta: \sa_{\alpha_1\beta_1}\cdot\ldots\cdot \sa_{\alpha_N\beta_N}
% =1
% \right\}
\label{eq:8}
\end{equation}
If we now assume that $\tau_{\vec\alpha}=1$, it follows from subtracting 
\eref{eq:sum:alpha:is:2N} from 
$\sum_{\vec\beta}\san_{\vec\alpha\vec\beta}\lambda_{\vec\beta}=2^N$ 
(which follows from the aforementioned assumption), 
% \begin{subequations}
% \begin{eqnarray}
% \sum_{\vec\beta}p_{\vec\beta}&=&1
% \label{eq:9a}\\
% \sum_{\vec\beta}\san_{\vec\alpha\vec\beta}p_{\vec\beta}&=&\tau_{\vec\alpha}=1
% \end{eqnarray}
% \label{eq:9}
% \end{subequations}
% that for all $\vec\beta\notin\Phi(\vec\alpha)$
\begin{eqnarray}
\lambda_{\vec\beta}=0,\quad \forall \vec\beta\notin\Phi(\vec\alpha).
\label{eq:condition:lambda:zero:Phi}
\end{eqnarray}
Thus, if $\tau_{\vec\alpha}=1$, then $\tau_{\vec\gamma}$
and $\tau_{\vec{\gamma^\prime}}$ are equal if
% , for all $\vec\beta\in\Phi(\vec\alpha)$.
\begin{equation}
\san_{\vbeta\vec\gamma}=\san_{\vbeta\vec{\gamma^\prime}}, \quad
\forall \vec\beta\in\Phi(\vec\alpha).
\label{eq:coneccion:dos:indices:A}
\end{equation}
% holds for all $\vec\beta\in\Phi(\vec\alpha)$. 
This follows from restricting the sum \eref{eq:tau:is:A:p}
to the $\lambda_\vbeta \ne 0$, given in \eref{eq:condition:lambda:zero:Phi}. 
Condition (\ref{eq:coneccion:dos:indices:A}) therefore connects three multi-indices, $\vec\alpha$,
$\vec\gamma$ and $\vec{\gamma^\prime}$.
When such a connection exists, $\tau_{\vec\alpha}=1$ implies
$\tau_{\vec\gamma}=\tau_{\vec{\gamma^\prime}}$. Let us now work out the nature
of this connection.

>>>>

\subsection{A vector space of channels} % {{{
\cpnote{Quiza falta lo de las clases de equivalencias}\janote{Pienso que sí porque
puede y debería ser útil para la sección siguiente de generadores.}\par
% Inversion de la relacion entre tau y p, y que las probablidiades deben ser positivas {{{
The problem of determining complete positivity of a PCE can be recast as 
determining which vectors $\vtau$ are mapped via
$\san$
% \begin{equation}
% \san\vec\tau=2^N\vec p
% \label{eq:condition}
% \end{equation}
to a vector with positive entries $\lambda_\valpha$, as in \eref{eq:lambda:is:A:tau}. 
\janote{Siento que hace falta un enunciado por aquí, al inicio de la sección, que haga
que el lector se pueda colgar de la idea de los espacios vectoriales. Quizás algo 
como}\janote{We will show how to associate unequivocally PCE quantum
channels with vector spaces.}
% . In components, this would read 
% \begin{equation}
% % \left(
% \sum_\vbeta
% \san_{\valpha\vbeta} \,
% % \right)
% \tau_{\vec \beta}=2^Np_{\vec\alpha}
% \label{eq:A:tau:is:p}
% \end{equation}
% where
% $\san_{\vec\alpha\vec\beta} =\sa_{\alpha_1\beta_1}\cdot\ldots\cdot
% \sa_{\alpha_N\beta_N}$. 
Using the fact that $a^{-1}=a/4$, so 
% (so $A = A^{-1}/2^N$) 
\begin{equation}
A^{-1} = \frac{1}{4^N} A
\end{equation}
we can directly invert \eref{eq:lambda:is:A:tau} to obtain 
\begin{equation}
% \tau_{\vec \alpha}= \san_{\vec\alpha\vec\beta} \, p_\vbeta,
% \tau = 
% \san \lambda =2^N \tau
\sum_\vbeta \san_{\valpha \vbeta} \lambda_\vbeta =2^N \tau_\valpha
\label{eq:tau:is:A:p}
\end{equation}
which will serve as a starting point for our analysis. 
This is a remarkable equation, as it provides a method to diagonalize any diagonal 
Pauli channel, as in \eref{eq:definition:Pauli}. \janote{por qué diagonalizar al 
canal de Pauli? Creo que sería más bien a la matriz de Choi, pero igual estoy 
un poco pérdido con el sentido del enunciado. }

Other two simple but crucial
observation are the following. For valid quantum channels, 
% \begin{equation}
% % \sum_{
% \end{equation}
$\sum_{\valpha \in \Omega} \lambda_\valpha=0$ implies that 
$\lambda_\valpha=0$ for all $\valpha\in \Omega$\janote{Qué es $\Omega$?}, as each member of the sum \janote{is}
greater or equal to zero, 
% $p_{\vec\alpha}+p_{\vec\beta}=0$ implies $p_{\vec\alpha}=p_{\vec\beta}=0$, as
% all $p_{\vec\alpha} \ge 0$
due to complete positivity of the underlying channel. 
Finally, looking into the first component of \eref{eq:tau:is:A:p}, and taking into 
account the normalization condition that $\tau_{\vec 0}=1$, we obtain
\begin{equation}
\sum_\valpha \lambda_\valpha = 2^N,
\label{eq:sum:alpha:is:2N}
\end{equation}
since, $A_{\vec 0, \vbeta}=1$ for all $\vbeta$. \par
% }}}
% Conexion de los indices para llegar al grupo de Klein {{{
Now we need a definition: to each multi-index $\vec\alpha$ we associate a \textit{set}
of multi-indices $\Phi(\vec\alpha)$ as follows
\begin{equation}
\Phi(\vec\alpha):=\left\{
\vec\beta:\san_{\vec\alpha\vec\beta}=1
\right\}
% =\left\{ \vec\beta: \sa_{\alpha_1\beta_1}\cdot\ldots\cdot \sa_{\alpha_N\beta_N}
% =1
% \right\}
\label{eq:8}
\end{equation}
If we now assume that $\tau_{\vec\alpha}=1$, it follows from subtracting 
\eref{eq:sum:alpha:is:2N} from 
$\sum_{\vec\beta}\san_{\vec\alpha\vec\beta}\lambda_{\vec\beta}=2^N$\janote{la resta no es al revés?}
(which follows from the aforementioned assumption), 
% \begin{subequations}
% \begin{eqnarray}
% \sum_{\vec\beta}p_{\vec\beta}&=&1
% \label{eq:9a}\\
% \sum_{\vec\beta}\san_{\vec\alpha\vec\beta}p_{\vec\beta}&=&\tau_{\vec\alpha}=1
% \end{eqnarray}
% \label{eq:9}
% \end{subequations}
% that for all $\vec\beta\notin\Phi(\vec\alpha)$
\begin{eqnarray}
\lambda_{\vec\beta}=0,\quad \forall \vec\beta\notin\Phi(\vec\alpha).
\label{eq:condition:lambda:zero:Phi}
\end{eqnarray}
Thus, if $\tau_{\vec\alpha}=1$, then $\tau_{\vec\gamma}$
and $\tau_{\vec{\gamma^\prime}}$ are equal if
% , for all $\vec\beta\in\Phi(\vec\alpha)$.
\begin{equation}
\san_{\vbeta\vec\gamma}=\san_{\vbeta\vec{\gamma^\prime}}, \quad
\forall \vec\beta\in\Phi(\vec\alpha).
\label{eq:coneccion:dos:indices:A}
\end{equation}
% holds for all $\vec\beta\in\Phi(\vec\alpha)$. 
This follows from restricting the sum \eref{eq:tau:is:A:p}
to the $\lambda_\vbeta \ne 0$, given in \eref{eq:condition:lambda:zero:Phi}. 
Condition (\ref{eq:coneccion:dos:indices:A}) therefore connects three multi-indices, $\vec\alpha$,
$\vec\gamma$ and $\vec{\gamma^\prime}$.
When such a connection exists, $\tau_{\vec\alpha}=1$ implies
$\tau_{\vec\gamma}=\tau_{\vec{\gamma^\prime}}$. Let us now work out the nature
of this connection.
